Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-19 MUSES_vs_BYOD_solutions.tex
Abstract improved
And also related to the title, which is not "Talk about Muses", but BYOD solutions.

Refs #29

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and particularly their Chief Security Officers (CSOs),
want to ensure that their Security Policies are complied, but this
goal turned hard to achieve since employees are able to use, or bring,
their personal devices at work. This has been named as ``Bring Your Own Device'' (BYOD). % <- Problem
As this BYOD philosophy is being adopted by many companies everyday, a number of solutions have appeared in the market, 
in order to adapt to it in a secure way. In this paper, a novel and open source system named
MUSES (Multiplatform Usable Endpoint Security), able 
to securely manage BYOD environments, is described. % <- Solution
MUSES has been developed to cope with security issues with regard to enterprise security policies, but as a user-centric tool. It considers users' behaviour in order to adapt, improve, or even increase the defined set of security rules. To do this, the system applies Machine Learning and Computational Intelligence techniques, being also able to predict future security incidences produced by these users. % <- Solution, details.
MUSES, which has released its first prototype this year, is compared with the most relevant
solutions offered by other companies to deal with the same issues as, remarking the advantages that our system offers with
respect to them. % <- we will explain why is better in the work

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and particularly their Chief Security Officers (CSOs),
want to ensure that their Security Policies are complied, but this
becomes a difficult goal to achieve at the point employees are able to use, or bring,
their personal devices at work, in a practice that has been named ``Bring Your
Own Device'' (BYOD). % <- Problem
Since this BYOD philosophy is being adopted by many companies
everyday, a number of solutions have appeared in the market so that it
can implemented in a secure way and comply with the Security Policies
mentioned above. In this paper we present an overview of BYOD security
solutions along a novel and open source system named
MUSES (Multiplatform Usable Endpoint Security), able 
to securely manage BYOD environments. % <- Solution
MUSES has been developed to cope with security issues with regard to
enterprise security policies, but as a user-centric tool. It considers
users' behaviour in order to adapt, improve, or even increase the
defined set of security rules. To do this, the system applies Machine
Learning and Computational Intelligence techniques, being also able to
predict future security incidences produced by these users. % <-
                                % Solution, details. 
MUSES, which has released its first prototype in early 2015, is
compared with the most relevant 
solutions offered by other companies to deal with the same issues as, remarking the advantages that our system offers with
respect to them. % <- we will explain why is better in the work
